r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2021-01-15 r-package/paper2020/paper2020.Rmd
minor paper tweaks

---
title: 'r5r: rapid realistic routing on multimodal transport networks with R5 in R'
author: "Rafael H. M. Pereira, Marcus Saraiva, Daniel Herszenhut, Carlos Kaue Braga"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
  html_document: default
abstract: Routing is a key step in transport planning. Nonetheless, researchers and practitioners face challenges to perform this task, such as the costs of licensed software and long computation times. Conveyal’s R<sup>5<\sup> is a multimodal transport network router that offers meaningful planning features, such as calculating travel times over a time window and returning multiple itineraries for a single or multiple origin/destination pairs. This paper describes r5r, an open source R package that leverages on R<sup>5<\sup> to allow users to efficiently compute travel time matrices and generate detailed itineraries between a set of origins and destinations at no expense.
urlcolor: blue
bibliography: references.json
---

@@

```{r, message = FALSE}
library(r5r)
library(sf)
library(data.table)
library(ggplot2)
library(akima)
```

@@

To account for variations on service levels accross the day [@stepniak2019impact], the user can use the `time_window` parameter. In this case, several matrices are calculated using one departure time every minute within the set time window. By default the function outputs the 50th percentile (i.e. the median) travel time between each origin and destination pair  within that time window. The `percentiles` parameter allows the user to retrieve travel time estimates at different points of the distribution. An example of the `travel_time_matrix()` function's usage is presented below:

@@

The plot below shows travel times from all origin points to the central bus station at five percentiles (20th, 40th, 60th, 80th, 99th), thus showing how the estimated travel times are more uncertain when leaving from some places than others. As expected, there is little to no uncertainty in travel times from places that are very close (walking distance) to the central bus station, while travel times from places that are far away are more affected by variations in the trip's departure time and service frequency levels.

@@

# reshape data
plot_data <- melt(ttm_tw, measure = patterns("^travel_time_p"), variable = "percentile", value = "travel_time")
plot_data[, mediantt := median(travel_time, na.rm=T), by=fromId]

@@

travel_times <- ttm[fromId %in% central_bus_stn$id ]
travel_times[points, on=c('toId' ='id'), `:=`(lon = i.lon, lat = i.lat)]
travel_times[, mediantt := median(travel_time_p020, travel_time_p040, 
                                  travel_time_p060, travel_time_p080,
                                  travel_time_p099), by = toId]

@@

The [R](https://github.com/conveyal/r5)<sup>5</sup> routing engine is developed at [Conveyal](https://www.conveyal.com/) with contributions from several developers. This work was supported by the Brazilian Institute for Applied Economic Research (Ipea).

>>>>

---
title: 'r5r: rapid realistic routing on multimodal transport networks with R5 in R'
author: "Rafael H. M. Pereira, Marcus Saraiva, Daniel Herszenhut, Carlos Kaue Braga"
date: "`r Sys.Date()`"
output:
   html_document: default
   word_document: default
   pdf_document: default
abstract: Routing is a key step in transport planning. Nonetheless, researchers and practitioners face challenges to perform this task, such as the costs of licensed software and long computation times. Conveyal’s R<sup>5</sup> is a multimodal transport network router that offers meaningful planning features, such as calculating travel times over a time window and returning multiple itineraries for a single or multiple origin/destination pairs. This paper describes r5r, an open source R package that leverages on R<sup>5</sup> to allow users to efficiently compute travel time matrices and generate detailed itineraries between a set of origins and destinations at no expense.
urlcolor: blue
bibliography: references.json
---

@@

```{r, message = FALSE, warning = FALSE}
library(r5r)
library(sf)
library(data.table)
library(ggplot2)
library(akima)
```

@@

To account for variations on service levels across the day [@stepniak2019impact], the user can use the `time_window` parameter. In this case, several matrices are calculated usinh every minute within the set time window as a departure time. By default the function outputs the 50th percentile (i.e. the median) travel time between each origin and destination pair  within that time window. The `percentiles` parameter allows the user to retrieve travel time estimates at different points of the distribution. An example of the `travel_time_matrix()` function's usage is presented below:

@@

The plot below shows travel times from all origin points to the central bus station at five percentiles (20th, 40th, 60th, 80th, 99th), thus showing how the estimated travel times are more uncertain when leaving from some places than others. As expected, there is little to no uncertainty in travel times from places that are very close (walking distance) to the central bus station, while travel times from places that are far away are more affected by variations in the departure time and service frequency levels.

@@

# reshape data
plot_data <- melt(ttm_tw, measure = patterns("^travel_time_p"), variable = "percentile", value = "travel_time")
plot_data[, mediantt := as.integer(median(travel_time, na.rm=T)), by=fromId]

@@

travel_times <- ttm[fromId %in% central_bus_stn$id]
travel_times[points, on=c('toId' ='id'), `:=`(lon = i.lon, lat = i.lat)]
travel_times[, mediantt := median(travel_time_p020, travel_time_p040, 
                                  travel_time_p060, travel_time_p080,
                                  travel_time_p099), by = toId]

@@

The [R<sup>5</sup>](https://github.com/conveyal/r5) routing engine is developed at [Conveyal](https://www.conveyal.com/) with contributions from several developers. This work was supported by the Brazilian Institute for Applied Economic Research (Ipea).
